---
title: "Real World Applications 5"
author: "Place your name here"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

# Load packages
library(tidyverse) # core
library(tidyquant) # financial analysis
library(lubridate) # time series
library(plotly)    # Interactive visualization

# Import charts
industry_indicators_fig   <- read_rds("../00_data/fig/industry_indicators_fig.rds")
```

# The vunerability assessment {.tabset .tabset-fade}

Analyze the data for your client company's industry and answer the following questions.

1.  How much have sales in the industry declined in the recession? What's the worst that has happened in the past?

***Place your answer here***

2.  Does the industry go into recession before, at the same time, or after the national economy goes into recession? If earlier or later, how many months of difference is there?

***Place your answer here***

3.  Does the industry recover from recession before, at the same time, or after the national economy? Again, what's the difference in months?

***Place your answer here***

4.  How long does the industry typically take to recover from a recession?

***Place your answer here***

```{r fig.height=6}
ggplotly(industry_indicators_fig)
```

# Business response to the questionnaire

***Question to the businesses*** Recessions raise the risk of bankruptcy. Even less severe downturns can limit the company's growth prospects for several years.

How does your company plan for a downturn?

***Response from businesses***

| Business              | Response from Business                                                                                                                                                                                                                                                                                                                                                                                                       |
|------------------|------------------------------------------------------|
| Graponne              | Our liquidity is a major focus when we are preparing for a downturn as well as our inventory levels.  Cash is king in terms of getting through a downturn. You also need great relationships with your lenders -- you hope they will stick with you when times get tough.                                                                                                                                                    |
| Bank of New Hampshire | The bank builds up loss reserves, conducts expense reviews, tries to maximize yield on assets, looks to sell less profitable assets, e.g. low yielding loans. The bank also conducts various annual stress tests and scenario analyses to identify potential problems that could arise during an adverse economic event. Corrective action is taken to mitigate these risks if the exposure is outside of acceptable ranges. |
| Comptus               | Our staffing is very light, and we utilize outsourcing when we are busy. In a downturn we can return to in house production.                                                                                                                                                                                                                                                                                                 |
