---
title: "Real World Applications 4"
author: "Place your name here"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

# Load packages
library(tidyverse) # core
library(tidyquant) # financial analysis
library(lubridate) # time series
library(plotly)    # Interactive visualization
library(patchwork) # rearranging multiple plots

# Import charts
input_output_price_fig <- read_rds("../00_data/fig/input_output_price_fig.rds")

```

         
# What is happening to your client business's profit margin?
Make your argument based on your analysis of the given charts. 

**Place your answer here**

```{r}
ggplotly(input_output_price_fig)

```

***Grappoone***

outputPrice = Consumer Price Index for All Urban Consumers: New Vehicles in U.S. City Average

inputPrice  = Producer Price Index by Industry: New Car Dealers: New Vehicle Sales

***Bank of New Hampshire***

outputPrice = Market Yield on U.S. Treasury Securities at 10-Year Constant Maturity

inputPrice  = Market Yield on U.S. Treasury Securities at 3-Month Constant Maturity

***Comptus***

outputPrice = Producer Price Index by Commodity: Machinery and Equipment: Miscellaneous Instruments

inputPrice  = Producer Price Index by Commodity: Metals and Metal Products: Nonferrous Metals
