---
title: "Week 5: Real World Applications 4"
author: "Place your name here"
date: "2022-09-17"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

# Load packages
library(tidyverse) # core
library(tidyquant) # financial analysis
library(lubridate) # time series
library(plotly)    # Interactive visualization

# Import charts
grappone_fig <- read_rds("fig/grappone_fig.rds")
comptus_fig  <- read_rds("fig/comptus_fig.rds")
bnh_fig      <- read_rds("fig/bnh_fig.rds")
```

# Economic Dashboard {.tabset .tabset-fade}

## Grappone

```{r}
ggplotly(grappone_fig)
```

outputPrice = Consumer Price Index for All Urban Consumers: New Vehicles in U.S. City Average

inputPrice  = Producer Price Index by Industry: New Car Dealers: New Vehicle Sales

## Bank of New Hampshire

```{r}
ggplotly(bnh_fig)
```

outputPrice = Market Yield on U.S. Treasury Securities at 10-Year Constant Maturity

inputPrice  = Market Yield on U.S. Treasury Securities at 3-Month Constant Maturity

## Comptus

```{r}
ggplotly(comptus_fig)
```

outputPrice = Producer Price Index by Commodity: Machinery and Equipment: Miscellaneous Instruments
         
inputPrice  = Producer Price Index by Commodity: Metals and Metal Products: Nonferrous Metals
         
# What is happening to your client business's profit margin?
Make your argument based on your analysis of the given charts. 
