---
title: "Week 3: Best Practices 2"
subtitle: "Ch2 Cycles in Your Sector of the Economy"
author: "Place your name here"
date: "2022-08-30"
output: 
  html_document: 
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

# Load packages
library(tidyverse)
library(tidyquant)
library(lubridate)
```

```{r}
# Import data

# symbols
symbols <- c("GDPC1", # real gdp
             "", # real corporate profits
             "PCECC96", # Real Personal Consumption Expenditures (consumer spending)
             "PCESVC96", # consumer services
             "PCDGCC96", # consumer durables
             "PCNDGC96", # consumer non-durables
             "PRFIC1", # Real Private Residential Fixed Investment (residential construction)
             "Y033RX1Q020SBEA", # capital spending on equipment and software
             "B009RX1Q020SBEA", # nonresidential construction
             "", # federal government spending excluding transfer payments
             "", # state and local government spending
             "", # exports
             "") # imports

# Download
data <- tq_get(symbols, 
              get = "economic.data",
              from = "1947-01-01")

# Recession data
Recession_Dates_tbl <- read_rds("data/Recession_Dates_tbl.rds")


# Transform data
data_clean <- data %>%
    
    group_by(symbol) %>%
    
    # Calculate percent change
    mutate(change = (price / lag(price))-1)  %>%
    mutate(text = str_glue("{date %>% quarter(type = 'year.quarter')},
                           Growth: {change %>% scales::percent(accuracy = 0.1)}"))

data_clean
```



```{r}
# Create a custom function to plot

plot_econ_series <- function(data_clean, var = "PRFIC1") {
    
    g <- data_clean %>%
    
    # Calculate percent change
    filter(symbol %in% c("GDPC1", 
                         var)) %>%
    
    # Plot
    ggplot(aes(date, change)) +
    geom_line(aes(color = symbol)) +
    geom_point(aes(text = text), size = 0.1, alpha = 0) +
    theme_tq() +
    theme(legend.position = "bottom",
          strip.text = element_text(size = 8),
          panel.grid.major.y = element_blank()) +

    geom_hline(yintercept = 0, color = "#18BC9C", size = 0.5, alpha = 0.7) +

    # Shade for recession
    geom_vline(data = Recession_Dates_tbl %>% filter(USREC == 1),
               aes(xintercept = as.numeric(date)), color = "#4876FF", alpha = 0.3) +

    labs(subtitle = "US Recessions in Blue Shade",
         y = "Percent",
         x = NULL)

    # Make the plot interactive 
    plotly::ggplotly(g, tooltip = "text")
    
}

```



# Chater Openning Questions

Managers need to know:

* 


# Solution


| your customers/products       | magnitude of spending changes | timing of spending changes  |
|------------------------|------------------------|------------------------|
| consumer services             | very stable                   | coincident with GDP         |
| consumer nondurables          | stable                        | coincident with GDP         |
| consumer durables             | volatile                      | coincident with GDP         |
| housing construction          | very volatile                 | leads fluctuations in GDP   |
| capital spending              | very volatile                 | lags fluctuations in GDP    |
| govt. spending, federal       | moderate                      | not always corr. with GDP   |
| govt. spending, state & local | stable                        | lags fluctuations in GDP    |
| exports                       | volatile                      | not corr. with GDP          |
| imports                       | volatile                      | varies depending on product |


# Historical Experience

```{r fig.cap="Gross Domestic Product", fig.align="center"}
data_clean %>% plot_econ_series(var = NULL)
```


# Profits across the Economic Cycle


# Consumer Spending

```{r fig.cap="GDP vs Consumer Spending", fig.align="center"}
data_clean %>% plot_econ_series(var = "PCECC96")
```


```{r fig.cap="GDP vs Consumer Services", fig.align="center"}
data_clean %>% plot_econ_series(var = "PCESVC96")
```


```{r fig.cap="GDP vs Consumer Durables", fig.align="center"}
data_clean %>% plot_econ_series(var = "PCDGCC96")
```


```{r fig.cap="GDP vs Consumer Non-Durables", fig.align="center"}
data_clean %>% plot_econ_series(var = "PCNDGC96")
```

# Housing

```{r fig.cap="GDP vs Nonresidential Construction", fig.align="center"}
data_clean %>% plot_econ_series(var = "PRFIC1")
```

# Capital Spending


# Government Spending


# Exports


# Imports


# Economic terms
Explan each of the following terms in your own words. The author explains the terms in the textbook. If necessary, you may also Google the term on the Web. Good resources include: 

* [The Economist](https://www.economist.com/economics-a-to-z?utm_medium=cpc.adword.pd&utm_source=google&utm_campaign=a.22brand_pmax&utm_content=conversion.direct-response.anonymous&gclid=Cj0KCQjwjvaYBhDlARIsAO8PkE2IxWRvG7BsEouDDKf1eZNsf2pkf-LVH0DpiNau-Yoa97rLRqujj_YaAvDCEALw_wcB&gclsrc=aw.ds)
* [Fun economic videos](https://www.youtube.com/user/mjmfoodie)

## Gross Domestic Product (GDP)
Explain the term in your own words here.

## Real versus nominal GDP
Explain the term in your own words here.

## Gross National Product (GNP)
Explain the term in your own words here.

## Recession
Explain the term in your own words here.

## Leading Indicators
Explain the term in your own words here.

# Economic events

## 2007 Great recession
Describe the event in your own words here. Include its causes and impacts on the economy and society. You may Google it and find information on the Web.




